### 2023-02-20 intro.qmd
update

The carbon flux leaving the surface layer for the ocean interior is referred to as the export flux [@Siegel2022-wd]. Historically, the export depth was usually set at 100 m but @Buesseler2020-sn strongly emphasized that carbon flux-related studies should now use the base of the euphotic zone (EZ, where there is enough light for primary production) as the export depth to clearly differentiate the layer where particulate organic carbon (POC) is produced (i.e. via photosynthesis) and where POC is consumed (i.e. remineralized). This remineralization (or respiration) consists in the conversion of organic matter back to inorganic forms (i.e. nutrients and DIC) by heterotrophic organisms [@Siegel2022-wd] such as zooplankton or fish.

@@

Estimates of global carbon export range between 5 and 12 Pg C year$^{-1}$ [@Dunne2007-mi; @Henson2011-mt; @Siegel2014-wg; @DeVries2017-wu; @Nowicki2022-no] with only 0.02-0.4 Pg C year$^{-1}$ reaching the sediment [@Dunne2007-mi; @Hayes2021-gg; @Nowicki2022-no] where carbon will be sequestered for millions of years. Almost all of the exported organic carbon will therefore be remineralized and sequestered away from the atmosphere on time scales ranging from months to millennia. [@Siegel2022-wd].

>>>>

The carbon flux leaving the surface layer for the ocean interior is referred to as the export flux [@Siegel2022-wd]. Historically, the export depth was usually set at 100 m but @Buesseler2020-sn strongly emphasized that carbon flux-related studies should now use the base of the euphotic zone (EZ, where there is enough light for net primary production (NPP)) as the export depth to clearly differentiate the layer where particulate organic carbon (POC) is produced (i.e. via photosynthesis) and where POC is consumed (i.e. remineralized). This remineralization (or respiration) consists in the conversion of organic matter back to inorganic forms (i.e. nutrients and DIC) by heterotrophic organisms [@Siegel2022-wd] such as zooplankton or fish.

@@

Estimates of global carbon export range between 5 and 12 Pg C year$^{-1}$ [@Laws2000-XX; @Dunne2007-mi; @Henson2011-mt; @Siegel2014-wg; @DeVries2017-wu; @Nowicki2022-no] with only 0.02-0.4 Pg C year$^{-1}$ reaching the sediment [@Dunne2007-mi; @Hayes2021-gg; @Nowicki2022-no] where carbon will be sequestered for millions of years. Almost all of the exported organic carbon will therefore be remineralized and sequestered away from the atmosphere on time scales ranging from months to millennia. [@Siegel2022-wd].

### 2023-02-20 observingCarbonCycle.qmd
update

# Modelling and observing the BCP {#sec-modelling-observing-BCP}

## Models

## Observation tools

@@

In order to fill the scarcity of data from research vessels and moorings as well as coping with surface-constrained satellite measurements, AUVs have been developed to take *in situ* measurements in all weathers and at all times, only being dependent on their battery life and ocean currents (for drifting AUVs).

>>>>

# Modeling and observing the BCP {#sec-modelling-observing-BCP}

## Biogeochemical models

The study of the BCP is of paramount importance to answer the question of how much carbon is exported and how much of the exported carbon will be sequestered? In order to achieve this goal, ocean modelers have developed different kinds of biogeochemical models to better quantify the different export pathways of the BCP.

![Top of the atmosphere (TOA) radiance is converted into remote sensing reflectance $R_{rs}(\lambda)$, which is the ratio of the solar radiation reflected from the surface of the ocean that penetrates the sea surface at a discrete wavelength $\lambda$. Using TOA and $R_{rs}(\lambda)$, primary products (yellow circles) can be derived (e.g. POC, inherent optical properties (IOP), chlorophyll (Chl) or sea surface temperature (SST). Those primary products can be used in numerical models (e.g. empirical relationships) to compute secondary products (orange and red circles) such as the phytoplankton commmunity composition (PCC), particle size spectra (PSS), phytoplankton carbon concentrations (C$_{phyto})$ and the NPP. Models (light blue circles) therefore incorporate primary and secondary products as well as ancillary data (red squares) either from satellite (e.g. SST), in situ data or model-based data (ocean circulation) to estimate carbon export and sequestration (dark blue circles). Figure taken from @Siegel2022-wd.](image/ObservingCarbonCycle/carbon_models.jpeg){#fig-bgc-models width="750" height="580"}

Because measuring directly the POC export flux would be challenging, it is common to estimate it as the fraction of the total NPP that is exported (i.e. export efficiency) [@Henson2011-mt].

::: {.blackbox data-latex=""}
::: {#box-npp .center data-latex=""}
A deeper look into net primary production
:::

Total net primary production includes new production (NP, mainly fueled from the upwelling of nitrogen from deeper water to the EZ) and regenerated production (RP, fueled with nitrogen recycled through the food web within the EZ) \[@Dugdale1967\].

@Eppley1979 introduced the f-ratio as follows

$$
f-ratio = \frac{NP}{NP+RP}
$$

In a steady state system, new production equals export production therefore the $f-ratio$ should be equal to the ratio of export production (EP) to total NPP, referred to as the $e-ratio$ by @laws2000-XX.

$$
e-ratio = \frac{EP}{NPP}
$$

define steady state?
:::

@box-npp

Empirical models likely represent the most straightforward option to estimate carbon export.

combining satellite observations and in situ measurements

Data-assimilated models

These models can either target the estimations of carbon export

These models (i.e. food-web, empirical and inverse models) incorporate satellite data (@sec-observation-tools), that can be defined as primary data product

numerical models based on simple empirical relationships to derive primary and secondary data products

As illustrated in @fig-bgc-models,

One of the key variable to estimate carbon export is the NPP. It has been used to compute the f-ratio, e-ratio -\> rentrer un peu là-dedans

The former

Henson2010

-   common approach = estimate fraction of total primary production that is exported (with f-ratio, Th234-ratio

-   encadré sur le f-ratio? en lien avec laws2000 ry Dugdale and Goering 1967

-   satellite data

Dunne2007

-   NPZD models (non exhaustive)

-   empirical models: predictor variables

-   empirical algorithm

Henson2011

-   Martin b : -0.86 (6 stations, in the NOrtheast Pacific), lack of data so b is generally assumed to be spatially constant and this b value has been applied in several biogeochemical models to describe the rate of particle reminrelaiation in the water column

-   data-derived algorithms

Siegel 2014

-   food-web model (e.g. NPZD)

-   estimation og floval exports by empirical extrapolations of field measurements or by using global coupled carboncyckle-pcean circualtion models but estimations of global export remain widely divergent

-   mechanisticlly, it is the flux of sinking carbon leaving the EZ that is relevant

-   e-ratio ? different du f-ratio?

-   satellite-based approach for assessing carbon export (thank you kostadinov 2009 and 2010) -\> slope of the particle size spectrum

-   mechanistic approach for estimating global carbon export using satellite observations and a food-web model

-   a complete assessment of carbon export from the surfce ocean must accout for this and other additional pathways

-   the BCP is more than just the export of carbon from the EZ. Understanding it, also requires the quantification of the vertical attenuation of the export flux below the EZ as well.

-   aller absoilument checker siegel 2022

Devries2017

Note perso

Ajouter Guidi 2015 pour une estimation de b regionale

## Observation tools {#sec-observation-tools}

@@

In order to fill the scarcity of data from research vessels and moorings as well as coping with surface-constrained satellite measurements, AUVs have been developed to take in situ measurements in all weathers and at all times, only being dependent on their battery life and ocean currents (for drifting AUVs).
